\section{Microphysics}\label{sec:microphys}
{\bf \Large
\begin{tabular}{ccc}
\hline
  Corresponding author & : & Yuta Kawai\\
\hline
\end{tabular}
}

To represent cloud-microphysics processes, 
we provide two microphysics schemes using SCALE library: 
three-class one-moment bulk and six-class one-moment bulk schemes.

In addition, 
a large-scale condensation scheme can be used. 
It is useful to investigate a feedback mechanism between the equations of motion and moisture within simplified physics.

\subsection{Three-class one-moment bulk scheme}
%%
As a three-class one-moment bulk microphysics scheme, 
the Kessler parameterization \citep{kessler_1969} can be used. 
In this scheme, 
the distribution function of particle size is expressed only by mass concentration. 
Considering two categories of water in cloud and rain, 
the ratios of the densities of cloud and rain to total air density are calculated.

The details of formulation are found in Section 8.3.1 of SCALE description \citep{scale_library}.

\subsection{Six-class one-moment bulk scheme}
%%
A six-class one-moment bulk microphysics scheme is based on \citet{tomita_2008}. 
This scheme calculates mass exchange among six categories of water substances, 
which are water vapor, cloud water, rain, cloud ice, snow, and graupel.  
Although the scheme largely follows \citet{lin_etal_1983}, 
the original method of \citet{lin_etal_1983} is modified as follows: 
Both cloud water and cloud ice are generated only by a saturation adjustment process, 
and wet growth process of graupel is omitted.
\citet{tomita_2008} indicates that these modifications result in 20\% reduction in computational cost 
without significant changes on physical performance.

The details of formulation are found in Section 8.3.2 of SCALE description \citep{scale_library}.


\subsection{Large-scale condensation scheme}
%
If the moisture content exceeds its saturation value,
the excess water vapor is converted to cloud water.
The associated latent heat is released to the atmosphere 
and the cloud water is removed with a certain timescale.
A typical value of timescale is set to about O($10^3$) seconds when the horizontal grid spacing is O($10^2$) km.

Based on approaches in some AGCMs, such as the Integrated Forecasting System (IFS) of the European Centre for Medium-Range Weather Forecasts \citep{tiedtke1987parametrization}, 
the formulation is described as follows.
If the specific humidity exceeds the saturation value $q_{v,s}$,
specific humidity $q_v$ is reduced toward $q_{v,s}$. 
The excess water vapor is converted to cloud water, which is removed as precipitation.
The temperature is increased by the release of latent heat. 

To calculate the adjusted state,
an implicit treatment is required because the $q_{v,s}$ is the function of temperature based on the Clausius-Clapeyron equation.
The tendencies of temperature and specific humidity are given by
%%
\begin{align*}
  \dfrac{T^{**} - T^*}{\tau_{\rm LSC}} &= \dfrac{L}{C_{p,d}} C_{\rm rate}, \\
  \dfrac{q_v^{**} - q_v^*}{\tau_{\rm LSC}} &= - C_{\rm rate},
\end{align*}
%%
where the double and single asterisks denote the adjusted and the unadjusted states, respectively;
$\tau_{\rm LSC}$ is the prescribed adjustment timescale for the large-scale condensation process;
$L$ is the latent heat of vaporization;
and $C_{\rm rate}$ is the condensation rate defined as
%%
\begin{align*}
  C_{\rm rate} = \dfrac{q_v^* - q_{v,s}(T^{**})}{\tau_{\rm LSC}}.
\end{align*}
%%
In idealized experiments, 
$q_{v,s}(T^*)$ is often linearized around $T^*$ as
%%
\begin{align*}
  q_{v,s}(T^{**}) \approx q_{v,s}(T^*) + \dfrac{dq_{v,s}}{dT}\Big|_{T=T^*} (T^{**} - T^*)
\end{align*}
%%
where $dq_{v,s}/dT$ is given by the Clausius-Clapeyron equation as
%%
\begin{align*}
  \dfrac{dq_{v,s}}{dT} \simeq \dfrac{L q_{v,s}}{R_v T^2}.
\end{align*}
%%
Then, the condensation rate is given by
%%
\begin{align}
  C_{\rm rate} = \dfrac{1}{\tau_{\rm LSC}} \; \dfrac{q_v^* - q_{v,s}(T^*)}{1 + \frac{L}{C_{p,d}} \frac{dq_{v,s}}{dT}\Big|_{T=T^*}}.
\end{align}
%%
For the diabatic heating in the density-weighted potential temperature in Eq.\,\eqref{eq:diabatic_heating} 
and the source terms in the mass equations of water vapor, 
we have
\begin{align}
  Q_{\rm LSC} &= \rho L C_{\rm rate}, \\
  S_{\rho q_v,{\rm LSC}} &= - \rho C_{\rm rate}.
\end{align}
