%------------------------------------------------------
\section{Turbulence}
\label{sec:basic_usel_turbulence}
%------------------------------------------------------
The turbulence scheme represents the sub-grid scale turbulent transport of momentum, heat, and tracers.
The turbulence component is activated by \nmitem{ATMOS_PHY_TB_DO} in \namelist{PARAM_ATMOS}.
The turbulence scheme and its calling interval are specified in \namelist{PARAM_ATMOS_PHY_TB}.

\editboxtwo{
\verb|&PARAM_ATMOS | & \\
\verb|ATMOS_PHY_TB_DO = .true.,| & ; Enable turbulence process \\
\verb|/ | & \\
}
\editboxtwo{
\verb|&PARAM_ATMOS_PHY_TB | & \\
\verb|TB_TYPE      = “SMAGORINSKY”,| & ; Choose from turbulence schemes in Table \ref{tab:tb_scheme_list} \\
\verb|TIME_DT      = 60.D0,|         & ; Time interval of turbulence process \\
\verb|TIME_DT_UNIT = “SEC”,|         & ; Unit for \verb|TIME_DT| \\
\verb|/ | & \\
}

The available choices of \nmitem{TB_TYPE} are listed in Table \ref{tab:tb_scheme_list}.
\nmitem{TIME_DT} and \nmitem{TIME_DT_UNIT} specify the time interval of the turbulence process.

%%%%%%%%%%%
\begin{table}[t]
\caption{Turbulence schemes available in \scaledg.}
\label{tab:tb_scheme_list}
\begin{center}
\begin{tabularx}{150mm}{lXX}
\hline
\rowcolor[gray]{0.9}
\verb|TB_TYPE| & Description & Note \\
\hline
\verb|SMAGORINSKY|         & Smagorinsky--Lilly type SGS turbulence scheme & for regional model \\
\verb|SMAGORINSKY_GLOBAL|  & Smagorinsky--Lilly type SGS turbulence scheme & for global model \\
\verb|DNS|                 & Constant viscosity and diffusivity & mainly for idealized experiments \\
\hline
\end{tabularx}
\end{center}
\end{table}
%%%%%%%%%%%


%------------------------------------------------------
\subsection{Smagorinsky--Lilly type scheme}
\label{subsec:physics_tb_smagorinsky}
%%
The Smagorinsky--Lilly type scheme is a sub-grid scale turbulence model based on \cite{smagorinsky1963general} and \cite{lilly1962numerical}.
The eddy viscosity is diagnosed from the local strain rate and a characteristic filter length.
The stratification effect is also taken into account following \cite{brown1994largeeddy}.
This scheme is suitable for large-eddy simulations and high-resolution experiments where sub-grid scale turbulent transport should be represented.
For the detailed formulation, refer to the model description.

The scheme-dependent parameters are specified in \namelist{PARAM_ATMOS_PHY_TB_DGM_SMG}.
%%
\editboxtwo{
\verb|&PARAM_ATMOS_PHY_TB_DGM_SMG | & \\
\verb|Cs             = 0.13D0,|    & ; Smagorinsky constant \\
\verb|NU_MAX         = 10000.D0,|  & ; Maximum eddy viscosity \\
\verb|filter_fac     = 2.0D0,|     & ; Factor for the filter length \\
\verb|consistent_tke = .true.,|    & ; Use TKE consistently in the SGS stress \\
\verb|/ | & \\
}
\nmitem{Cs} specifies the Smagorinsky constant.
\nmitem{NU_MAX} specifies the upper limit of eddy viscosity.
\nmitem{filter_fac} controls the characteristic filter length used in the SGS model.
\nmitem{consistent_tke} controls whether the parameterized turbulent kinetic energy is included consistently in the SGS stress.


The parameterized eddy viscosity, eddy diffusivity, and turbulent kinetic energy can be output as history variables, 
for example, \verb|NU|, \verb|KH|, and \verb|TKE|.


%------------------------------------------------------
\subsection{Smagorinsky--Lilly type scheme for global model}
\label{subsec:physics_tb_smagorinsky_global}
%%
The scheme-dependent parameters are specified in \namelist{PARAM_ATMOS_PHY_TB_DGM_GLOBALSMG}.
%%
\editboxtwo{
\verb|&PARAM_ATMOS_PHY_TB_DGM_GLOBALSMG | & \\
\verb|Cs             = 0.13D0,|    & ; Smagorinsky constant \\
\verb|NU_MAX         = 10000.D0,|  & ; Maximum eddy viscosity \\
\verb|filter_fac     = 2.0D0,|     & ; Factor for the filter length \\
\verb|consistent_tke = .true.,|    & ; Use TKE consistently in the SGS stress \\
\verb|/ | & \\
}
%%
The parameters have the same meaning as those in \namelist{PARAM_ATMOS_PHY_TB_DGM_SMG}.
The global version should be used with the global dynamical core.


%------------------------------------------------------
\subsection{Constant viscosity and diffusivity}
\label{subsec:physics_tb_dns}
%%
For idealized experiments or direct numerical simulations (DNS), 
constant viscosity and diffusivity can be used by setting \nmitem{TB_TYPE} to \verb|DNS|.
%%
\editboxtwo{
\verb|&PARAM_ATMOS_PHY_TB | & \\
\verb|TB_TYPE      = “DNS”,| & ; Constant viscosity and diffusivity \\
\verb|TIME_DT      = 60.D0,| & ; Time interval of turbulence process \\
\verb|TIME_DT_UNIT = “SEC”,| & ; Unit for \verb|TIME_DT| \\
\verb|/ | & \\
}

The scheme-dependent parameters are specified in \namelist{PARAM_ATMOS_PHY_TB_DGM_DNS}.
%%
\editboxtwo{
\verb|&PARAM_ATMOS_PHY_TB_DGM_DNS | & \\
\verb|DNS_NU = 0.D0,| & ; Constant viscosity \\
\verb|DNS_MU = 0.D0,| & ; Constant diffusivity \\
\verb|/ | & \\
}
