%------------------------------------------------------
\section{Surface flux}
\label{sec:basic_usel_surface_flux}
%------------------------------------------------------

Surface fluxes represent the exchange of momentum, heat, and moisture
between the surface and the atmosphere.
Surface fluxes are configured by two namelists.
First, the surface flux component is activated by \nmitem{ATMOS_PHY_SF_DO} in \namelist{PARAM_ATMOS}.
Then, the surface flux scheme and its calling interval are specified in \namelist{PARAM_ATMOS_PHY_SFC}.

\editboxtwo{
 \verb|&PARAM_ATMOS | & \\
 \verb|ATMOS_PHY_SF_DO = .true.,| & ; Enable surface flux process \\
 \verb|/ | & \\
}
\editboxtwo{
 \verb|&PARAM_ATMOS_PHY_SFC | & \\
 \verb|SFCFLX_TYPE  = "CONST",| & ; Choose from surface flux schemes in Table \ref{tab:sfcflx_scheme_list} \\
 \verb|TIME_DT      = 60.D0,|   & ; Time interval of surface flux process \\
 \verb|TIME_DT_UNIT = "SEC",|   & ; Unit for \verb|TIME_DT| \\
 \verb|/ | & \\
}

The available choices of \nmitem{SFCFLX_TYPE} are listed in Table \ref{tab:sfcflx_scheme_list}.
The constant surface-flux scheme uses the corresponding SCALE library component, and its parameters are configured as in SCALE-RM.
\nmitem{TIME_DT} and \nmitem{TIME_DT_UNIT} specify the time interval of the surface-flux process.


%%%%%%%%%%%
\begin{table}[t]
\caption{Surface flux schemes available in \scaledg.}
\label{tab:sfcflx_scheme_list}
\begin{center}
\begin{tabularx}{150mm}{lX}
\hline
\rowcolor[gray]{0.9}
\verb|SFCFLX_TYPE| & Description \\
\hline
\verb|CONST|  & Constant surface-flux scheme \\
\verb|SIMPLE| & Simple bulk surface-flux scheme with constant bulk coefficients \\
\hline
\end{tabularx}
\end{center}
\end{table}
%%%%%%%%%%%

The surface temperature used in the surface-flux calculation is stored as \nmitem{SFC_TEMP}.
If no other component updates it, its default value can be specified by \nmitem{ATMOS_PHY_SFC_DEFAULT_SFC_TEMP} in \namelist{PARAM_ATMOS_PHY_SFC} as 
\editboxtwo{
 \verb|&PARAM_ATMOS_PHY_SFC | & \\
 \verb|ATMOS_PHY_SFC_DEFAULT_SFC_TEMP = 300.D0,| & ; Default surface temperature [K] \\
 \verb|/ | & \\
}

The surface flux variables can be output as history variables.
For example, \verb|SFLX_MU|, \verb|SFLX_MV|, and \verb|SFLX_MW| are
the momentum fluxes, \verb|SFLX_SH| and \verb|SFLX_LH| are the sensible
and latent heat fluxes, and \verb|SFLX_QV| is the water vapor flux.
The surface temperature is output as \verb|SFC_TEMP|.


%------------------------------------------------------------------------
\subsection{Constant surface-flux scheme}
\label{subsec:physics_sf_const}
%%
This scheme prescribes horizontally uniform sensible and latent heat fluxes.
The surface momentum flux is calculated using prescribed parameters such as a bulk coefficient for momentum or friction velocity.
This option is useful for idealized experiments where simple surface forcing is sufficient.
This scheme uses the SCALE library, 
and its parameters are configured by \namelist{PARAM_ATMOS_PHY_SF_CONST} as in SCALE-RM.


%------------------------------------------------------------------------
\subsection{Simple bulk surface-flux scheme}
\label{subsec:physics_sf_simple}
%%
This scheme calculates surface momentum, sensible heat, and latent heat fluxes using constant bulk coefficients.
The surface moisture is diagnosed from the surface temperature and surface pressure with an evaporation efficiency.
This option is useful for idealized experiments where the surface fluxes should depend on the near-surface atmospheric state 
while keeping the parameterization simple.

The scheme-dependent parameters are specified in \namelist{PARAM_ATMOS_PHY_SF_SIMPLE}.
%%
\editboxtwo{
 \verb|&PARAM_ATMOS_PHY_SF_SIMPLE | & \\
 \verb|ATMOS_PHY_SF_CONST_CM  = 1.1D-3,| & ; Constant bulk coefficient for momentum \\
 \verb|ATMOS_PHY_SF_CONST_CH  = 4.4D-3,| & ; Constant bulk coefficient for heat \\
 \verb|ATMOS_PHY_SF_CONST_CE  = 4.4D-3,| & ; Constant bulk coefficient for evaporation \\
 \verb|ATMOS_PHY_SF_BULK_BETA = 1.0D0,|  & ; Evaporation efficiency \\
 \verb|ATMOS_PHY_SF_U_MINM    = 0.D0,|   & ; Minimum wind speed for surface fluxes [m/s] \\
 \verb|/ | & \\
}
